---
title: "Simple"
author: "Mia Yu"
date: "2023-09-12"
output: 
  html_document:
   toc: true
   toc_float: true
   code_folding: hide
   
---

```{r}
library(tidyverse)
```

# Section 1: First Chunk

Here's a **code chunk** that samples from 
a_normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2: Make a plot

This code is borrowed from last lecture;

```{r}
plot_df = 
  tibble(
    x=rnorm(1000, sd = 0.5),
    y = 1 + 2 * x + rnorm(1000)
  )
```

Next up is a histogram of `x` variable in `plot_df`.

```{r}
ggplot(plot_df, aes(x = x)) + geom_histogram()
```

Lastly, I will do a scatterplot.

```{r}
ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```

here's a list:

* this is the first list thing
* here's another list item

# Section 3: Learning assessment!

```{r la_df}
la_df= 
  tibble(
    num_samp = rnorm(500, mean = 1),
    log_vec = num_samp > 0,
    abs_val = abs(num_samp)
  )

ggplot(la_df, aes(x = abs_val)) + geom_histogram()
```


# Section 4: Text formatting examples

Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell